{ \normalsize Master Thesis} \\ Bluetooth Low Energy Supported Indoor Location

### 2017-03-21 paper.tex
Abstract

	Abstract

@@

%INSERT FUNCTION AND EXPLAINATION.

>>>>

Nowadays there is a great demand for positioning systems and while the outdoor perfomance is amazing through the use of GPS, indoor positioning systems have been studied in order to also achieve such results. In this paper one studies the actual state of indoor systems, through an analysis on the usable technologies and techniques, and makes a critical analysis through a modern prespective centered on location services through smartphones. Since there is a great number of different indoor location systems, one found a need to create an framework capable of hosting such systems in the form of a smartphone-centric architecture, where interoperability would attempt to be achieved through the externalization of the main components of indoor systems. As such GEFILOC, a generic framework for indoor location systems which would allow for system that made use of it, to be capable of operating together on the same device without additional requirements , is proposed and a Bluetooth low energy-based system is implemented. This implementation allows for analysing the energetic costs of the architecture and comprehending how to set up one or more systems for analysing the interoperability component.

@@
